\section{Introduction}

Recent years have a seen a rapid growth in the adoption of serverless computing
by industry. Serverless platforms, pioneered by AWS Lambda, offer a combination
of zero up-front cost, low maintenance, and a pay-as-you-go pricing model that
allows low-cost software deployment % Cite papers on serverless savings.

Serverless platforms, also known as Functions-as-a-Service (FaaS), are cloud
computing services that let users upload functions to the cloud, and define
events, such as http requests, that trigger those functions. The cloud provider
is then responsible for monitoring events, instantiating the execution
environment (e.g. spinning up a vm that matches the function requirements), and
invoking the function on the event inputs. 

In order to facilitate this execution model, serverless functions must conform
to some technical restrictions: serverless functions must be stateless, and
short-lived. Serverless platforms do not make any guarantees on the reuse of
execution environments, and consequently, a developer cannot rely on the state
of the execution being preserved across invocations. Additionally, for technical
reasons serverless function execution running times are capped (300s for most
cloud providers).

The main difference between serverless applications and traditional, monolithic
applications is the event-driven programming model. While event-driven
programming exists since at least the early 90s, it has not gained popularity
outside of the domains of GUI and hardware programming. The main barrier for
adoption being the the non-standard programming model, and the complexity of
debugging event-driven applications. The vicious cycle of lack of popularity
that leads to a lack of proper tooling that would otherwise ease the development
process certainly did not help.

The advent of serverless computing, with its myriad of benefits, seems to be
forcing the hand of programmers and finally pushing event-driven programming
into the mainstream. Once software developers migrate to serverless computing,
however, they are forced to contend with this lack of debug tools, on top of the
need to switch programming paradigms. Consequently, they tend to resort to the
most basic debug technique know to man---log printouts.

The already-hard problem of debugging event-driven application is made
significantly harder by the setting of serverless computing. The ephemeral
nature of serverless function executions means that it is impossible to
determine, a-priori, on which machine a function will be executed. This makes
traditional techniques of remotely connecting to a running execution impossible
to apply to the serverless setting without explicit support from the platform
providers. Additionally, strict function timeouts mean that even if you
successfully connect to a running function, debugging it is a race against the
clock. Making matters even worse is the fact that no provider currently gives
the option of freezing the execution of the entire system, as is common when
debugging traditional multi-threaded applications. Thus, it is impossible to get
a snapshot of the whole system state, which significantly complicates the task
of understanding the behaviour of the system as a whole.

The reliance on databases to store the program state of serverless applications
brings to the forefront the problem of data provenance tracking---the ability to
identify, given a datum, the specific function invocation that produced that
datum. Consider for example a debug session in which the programmer steps
through an execution of a serverless function, and encounters a failure that is
the result of an unexpected value stored in the database. In order to continue
the debug process and discover the root cause of this failure, the user needs to
determine what was the function execution that wrote this unexpected value to
the database, and debug that function. In a local setting, where most shared
state is stored in memory, all a user would have to do is rerun the execution
with a conditional breakpoint that breaks the execution when a specific value is
written to a specific variable. However, the serverless setting does not provide
any way to rerun the execution (even when the bug is reproducible), or add
variable watches or breakpoints. Following such a sequence of data provenance
investigations to the root cause of the bug is a near-sisyphean undertaking.

Finally, the cloud setting usually involves the use of cloud services, which
often provide relaxed consistency guarantees. For example, amazon's DynamoDB
provides an eventual-consistency wherein data writes \emph{usually} propagate
within 1 second. These consistency guarantees may lead to subtle bugs that occur
or as a result of unexpected function invocation timings. This is true even when
developers are fully aware of the consistency guarantees and plans for them, let
alone in the arguably more common case of developers failing to account for
unconventional consistency guarantees. 

In this work we set about to closing this gap. We introduce \system, a
\emph{record and replay} system for recording the execution of serverless
applications in active deployment. \system lets the user rerun locally any
function invocation in a way that faithfully recreates the function execution on
the cloud. The user can then use a debugger to debug the execution of the
function in the same way they would debug a monolithic application. When the
user encounters an unexpected value in the database (an unexpected result of a
database read call) \system provides the capabilities to jump to the function
that originally wrote that to the database, and debug that function.
Additionally, \system automatically detects inconsistent reads that may have
resulted from the lax consistency guarantees made by the system, thus bringing
this source of potential problems to the forefront of developer's attention.

\subsection{Recording Serverless Application Executions}
\subsection{Replaying Serverless Application Executions}
\subsection{Database Time-Travel}

\paragraph{Limitations}
In this work we focus on serverless applications composed of Node.js functions.

% A few paragraphs on the proposed solution
%
%   First, an explanation of the recording framework
%
%   Second, a discussion on the replay part of the framework
%      * Replay of a single (stateless) function
%      * Handling state in functions
%      * Data provenance causality jumps
%
%   Third, handling databases
%
